An Object-Logic Explanation for the Inconsistency in G\"odel's Ontological Theory

### 2016-07-11 Papers/2016/KI/main.tex
Compress proof note

\title{An Object-Logic Explanation for the Inconsistency in G\"odel's Ontological Theory}
\author{Christoph Benzm\"uller\inst{1}\thanks{This work has been supported by
    the German Research Foundation DFG under grants BE2501/9-1,2} \and Bruno Woltzenlogel Paleo\inst{2} 
}

>>>>

\title{An Object-Logic Explanation for the Inconsistency in G\"odel's Ontological Theory}
\author{Christoph Benzm\"uller\inst{1}\thanks{This work was supported by
    the German Research Foundation DFG grant BE2501/9-1,2} \and Bruno Woltzenlogel Paleo\inst{2} 
}
